---
title: "log"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

* NO need to worry about NAMESPACE for now
* if in usages, genertic and class are not separated, search and replace >> {generic -> {generic}{

STEPS
* imports for last

* Open the mixOmics project
* sort R files by names and open the top one that hasn't been converted - look at the last commit
* open its counterpart in buildignore/RD2Roxygen
* Put its documention in source
* Drop the headers, edit authors
* Drop usage and alias(?)
* Add appropriate @name (generic), @rdname, and @export tags, remove @usage if @export does not generate it as it should
* reformat the code
* separate examples
* remove the old Rd file
* create the new one using Roxygen2
* Watch out for the ones in ./man that are not an R file name
* commit message
    roxygenated: foo
```{r}
#' @example ./examples/foo-examples.R
#' Kim-Anh Lê Cao, Al J Abadi
#' @name
#' @rdname
#' @export
```

# TODO

* Deprecate estim.regul in favour of tune.rcc https://mirai-solutions.ch/news/2017/12/05/roxygen2-deprecate/ and document how to deprecate and defunct
* remeber estim.regul will be there cause there's no source making it now
* transfer `plot.tune.rcc` to plot methods
* document `imageMap`


