---
description: |
  "This is a child document for README.Rmd to isolate What's New updates (last section of README)"
  "see README.Rmd's last chunk."
  "No need to knit this. Knitting README will automatically include this."
---

```{r setup-news, include=FALSE}
library(knitr)
opts_chunk$set( echo = TRUE, eval = FALSE, warning = FALSE, message = FALSE)
```


```{r, echo=FALSE, eval=FALSE, message='hide', fig.asp=1, out.width="50%"}
## template chunk - don't change/delete
```

## What's New

#### March 2022

* bug fix implemented for [Issue #196](https://github.com/mixOmicsTeam/mixOmics/issues/196). `perf()` can now handle features with a `(s)pls` which have near zero variance.
* bug fix implemented for [Issue #192](https://github.com/mixOmicsTeam/mixOmics/issues/192). `predict()` can now handle when the testing and training data have their columns in different orders.
* bug fix implemented for [Issue #178](https://github.com/mixOmicsTeam/mixOmics/issues/178). If the `indY` parameter is used in `block.spls()`, `circosPlot()` can now properly identify the $Y$ dataframe.
* bug fix implemented for [Issue #172](https://github.com/mixOmicsTeam/mixOmics/issues/172). `perf()` now returns values for the `choice.ncomp` component when `nrepeat` $< 3$ whereas before it would just return `NA`s.
* bug fix implemented for [Issue #171](https://github.com/mixOmicsTeam/mixOmics/issues/171). `cim()` now can take `pca` objects as input.
* bug fix implemented for [Issue #161](https://github.com/mixOmicsTeam/mixOmics/issues/161). `tune.spca()` can now handle `NA` values appropriately.
* bug fix implemented for [Issue #150](https://github.com/mixOmicsTeam/mixOmics/issues/150). Provided users with a specific error message for when `plotArrow()` is run on a `(mint).(s)plsda` object.
* bug fix implemented for [Issue #122](https://github.com/mixOmicsTeam/mixOmics/issues/122). Provided users with a specific error message for when a `splsda` object that has only one sample associated with a given class is passed to `perf()`.
* bug fix implemented for [Issue #120](https://github.com/mixOmicsTeam/mixOmics/issues/120). `plotLoadings()` now returns the loading values for features from **all** dataframes rather than just the last one when operating on a `(mint).(block).(s)plsda` object.
* bug fix implemented for [Issue #43](https://github.com/mixOmicsTeam/mixOmics/issues/43). Homogenised the way in which `tune.mint.splsda()` and `perf.mint.splsda()` calculate balanced error rate (BER) as there was disparity between them. Also made the global BER a weighted average of BERs across each study.
* enhancement implemented for [Issue #30/#34](https://github.com/mixOmicsTeam/mixOmics/issues/34). The parameter `verbose.call` was added to most of the methods. This parameter allows users to access the specific values input into the call of a function from its output.
* bug fix implemented for [Issue #24](https://github.com/mixOmicsTeam/mixOmics/issues/24). `background.predict()` can now operate on `mint.splsda` objects and can be used as part of `plotIndiv()`.

#### July 2021

* new function `plotMarkers` to visualise the selected features in block analyses (see https://github.com/mixOmicsTeam/mixOmics/issues/134)
* `tune.spls` now able to tune the selected variables on both `X` and `Y`. See `?tune.spls`
* new function `impute.nipals` to impute missing values using the nipals algorithm
* new function `tune.spca` to tune the number of selected variables for pca components
* `circosPlot` now has methods for `block.spls` objects. It can now handle similar feature names across blocks. It is also much more customisable. See advanced arguments in `?circosPlot`
* new `biplot` function for `pca` and `pls` objects. See `?mixOmics::biplot`
* `plotDiablo` now takes `col.per.group` (see #119)

#### April 2020

* weighted consensus plots for DIABLO objects now consider per-component weights

#### March 2020

* `plotIndiv` now supports (weighted) consensus plots for block analyses. See the example in [this issue](https://github.com/mixOmicsTeam/mixOmics/issues/57)
* `plotIndiv(..., ind.names=FALSE)` [warning issue](https://github.com/mixOmicsTeam/mixOmics/issues/59) now fixed

#### January 2020

* `perf.block.splsda` now supports calculation of combined AUC
* `block.splsda` bug which could drop some classes with `near.zero.variance=TRUE` now fixed
