---
description: |
  "This is a child document for README.Rmd to isolate What's New updates (last section of README)"
  "see README.Rmd's last chunk."
  "No need to knit this. Knitting README will automatically include this."
---

```{r setup-news, include=FALSE}
library(knitr)
opts_chunk$set( echo = TRUE, eval = FALSE, warning = FALSE, message = FALSE)
```


```{r, echo=FALSE, eval=FALSE, message='hide', fig.asp=1, out.width="50%"}
## template chunk - don't change/delete
```

## What's New

#### July 2021

* new function `plotMarkers` to visualise the selected features in block analyses (see https://github.com/mixOmicsTeam/mixOmics/issues/134)
* `tune.spls` now able to tune the selected variables on both `X` and `Y`. See `?tune.spls`
* new function `impute.nipals` to impute missing values using the nipals algorithm
* new function `tune.spca` to tune the number of selected variables for pca components
* `circosPlot` now has methods for `block.spls` objects. It can now handle similar feature names across blocks. It is also much more customisable. See advanced arguments in `?circosPlot`
* new `biplot` function for `pca` and `pls` objects. See `?mixOmics::biplot`
* `plotDiablo` now takes `col.per.group` (see #119)

#### April 2020

* weighted consensus plots for DIABLO objects now consider per-component weights

#### March 2020

* `plotIndiv` now supports (weighted) consensus plots for block analyses. See the example in [this issue](https://github.com/mixOmicsTeam/mixOmics/issues/57)
* `plotIndiv(..., ind.names=FALSE)` [warning issue](https://github.com/mixOmicsTeam/mixOmics/issues/59) now fixed

#### January 2020

* `perf.block.splsda` now supports calculation of combined AUC
* `block.splsda` bug which could drop some classes with `near.zero.variance=TRUE` now fixed
