---
description: |
  "This is a child document for README.Rmd to isolate What's New updates (last section of README)"
  "see README.Rmd's last chunk."
  "No need to knit this. Knitting README will automatically include this."
---

```{r setup-news, include=FALSE}
library(knitr)
opts_chunk$set( echo = TRUE, eval = FALSE, warning = FALSE, message = FALSE)
```


```{r, echo=FALSE, eval=FALSE, message='hide', fig.asp=1, out.width="50%"}
## template chunk - don't change/delete
```

## What's New

#### November 2019

* Parallel computing improved for `tune` and `perf` functions, and even more on Unix-like systems.

```{r, eval=FALSE, echo=FALSE}
library(mixOmics)
require(microbenchmark)
require(parallel)
data(nutrimouse)
nrep <- 25
folds <- 2
Y = nutrimouse$diet
data = list(gene = nutrimouse$gene, lipid = nutrimouse$lipid)
design = matrix(c(0,1,1,1,0,1,1,1,0), ncol = 3, nrow = 3, byrow = TRUE)

nutrimouse.sgccda <- block.splsda(X=data,
                                  Y = Y,
                                  design = design,
                                  keepX = list(gene=c(10,10), lipid=c(15,15)),
                                  ncomp = 2,
                                  scheme = "horst")
microbenchmark::microbenchmark(
  serial =  perf(nutrimouse.sgccda, folds = folds, nrepeat = nrep),
  parallel =  perf(nutrimouse.sgccda, folds = folds, nrepeat = nrep, cpus = parallel::detectCores()), times = 2
)
#> Unit: seconds
#>      expr      min       lq      mean    median        uq       max neval
#>    serial 10.09760 10.09760 12.130116 12.130116 14.162629 14.162629     2
#>  parallel  5.62336  5.62336  5.756024  5.756024  5.888689  5.888689     2
```

  
  
* Fixed margin error problem with `plotLoadings`. See the example in [this issue](https://github.com/mixOmicsTeam/mixOmics/issues/45).
* `cim` bug which overestimated correlations for single component now fixed.
* `perf.sgccda` now supports calculation of average combined AUC.

```{r, eval=FALSE, echo=FALSE}
library(mixOmics)
data(nutrimouse)
nrep <- 4
folds <- 4
Y = nutrimouse$diet
data = list(gene = nutrimouse$gene, lipid = nutrimouse$lipid)
design = matrix(c(0,1,1,1,0,1,1,1,0), ncol = 3, nrow = 3, byrow = TRUE)
set.seed(42)
nutrimouse.sgccda <- block.splsda(X=data,
                                  Y = Y,
                                  design = design,
                                  keepX = list(gene=c(10,10), lipid=c(15,15)),
                                  ncomp = 2)

perf.res <- perf(nutrimouse.sgccda, folds = folds, nrepeat = nrep, 
     auc = TRUE, cpus = parallel::detectCores())

perf.res$auc
#> $comp1
#>                        AUC   p-value
#> coc vs Other(s)  0.8769531 0.2125844
#> fish vs Other(s) 0.6914062 0.4333581
#> lin vs Other(s)  0.5449219 0.5615303
#> ref vs Other(s)  0.5000000 0.5086909
#> sun vs Other(s)  0.6640625 0.4005816
#> 
#> $comp2
#>                        AUC   p-value
#> coc vs Other(s)  0.9179688 0.1401584
#> fish vs Other(s) 0.8164062 0.2083663
#> lin vs Other(s)  0.7089844 0.3245500
#> ref vs Other(s)  0.5800781 0.4885250
#> sun vs Other(s)  0.9238281 0.1132753
```

#### September 2019

* You can now customise `auroc` plots in version 6.8.3. See example [here](https://github.com/mixOmicsTeam/mixOmics/issues/35).

####  August 2019

* The infamous `plot.perf` bug has been fixed in version 6.8.2. See example [here](https://github.com/mixOmicsTeam/mixOmics/issues/27).



